---
title: "workshop2"
author: "Krrish"
format: 
  html :
    theme: "cerulean"
  pdf:
     toc: true
editor: visual
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE
  )
```

```{r}
library(rmarkdown)
library(knitr)
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)


```

```{r}
getwd()
dat <- read_csv("avian_influenza_numbers.csv")

```

```{r}
head(dat)
```

```{r}
dat %>%
  head(10)
```

```{r}
glimpse(dat)

?glimpse()
```

```{r}
str(dat)
```

```{r}
dim(dat)

```

`` `r nrow(dat)` ``

`` `r ncol(dat)` ``

`###`Why is it important to know the dimension of your dataset?

-   Is my data complete or did some rows fail to load?

-   Do I have enough data to draw conclusions? (10 rows vs 10 million rows is very different)

-   After filtering, did I accidentally delete too many rows?

`###`What are the variable names in the dataset? \
use name function to print all the coloum names\
\[1\] "Range" "Month" "Vietnam" "Turkey" "Thailand" "Iraq"\
\[7\] "Indonesia" "Egypt" "Djibouti" "China" "Cambodia" "Nigeria"\
\[13\] "Azerbaijan" "Pakistan" "Myanmar" "Laos" "Bangladesh" "Canada"\
\[19\] "India" "Nepal" "United Kingdom" "Spain" "United States" "Ecuador"\
\[25\] "Chile" "Australia"\
\>

`Australia : The number of influenza count`

#Ex 4

```{r}
library(lubridate)
data_cleaned <- dat |>
  select(Month,Australia, Egypt,`United States`) |>
  mutate(Month = mdy(Month) |>
  filter(!is.na(Month))
           
           

```

```{r}
library(kableExtra)
summarise()
```

\

# Introduction

In this tutorial we are looking at the Avian Influenza cases detected globally since 1997.

[US CDC](https://www.cdc.gov/bird-flu/php/avian-flu-summary/chart-epi-curve-ah5n1.html)
